---
title: "demmap"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{demmap}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#library(demmap)
```



**demmap** is for mappings between arrays.

demmap is a dependency for demarray, and doesn't know about concepts introduced in demarray, eg Values vs Counts, or dimtypes. demmap ignores any dimnames.

demarray can impose extra restrictions on A and B that demmap does not know about.

## Setup

Let $X$ be an array. $X$ has dimensions $d_k, k = 1, \dots, K$. Elements of $X$ can be specified using the $K$-dimensional index $(m_1, \dots, m_K)$, or the one-dimensional index $i$, $1 \le i \lt I = \prod_{k=1}^K d_k$.

Let $s_k = \prod_{v=0}^k d_v$ be the "stride" for the $k$th dimension. Then the $K$-dimensional and one-dimensional indices are related as follows:
\begin{equation}
  i - 1 = \sum_{k=1}^K s_k (m_k - 1).
\end{equation}



## Arrays A and B

have at least one shared dimension
A can have dimensions not in B, and B can have dimensions not in A.
A-shared and B-shared are arrays formed from shared dimensions.



Each position along a dimension of A-shared can map on to 0 or one positions along the corresponding dimension of B-shared. Each position along an element of B-shared can map on to 0, 1, or more elements of teh corresponding dimension of A-shared.




## Conventions in R code

By default, use 1-based indices. If using 0-based index, name it accordingly.


i - 1-dimensional index , ie position within A treated as vector. 
j - 1-diemnsional index, ie position within B treated as a vector.
I - length of A, treated as a vector. equal to prod(dim_A)
J - length of B, treated as a vector. equal to prod(dim_A)

dim - lengths of dimensions (ie standard R definition)
K - the length of dim
k - index for dim, k = 1, ..., K
d - the length of the k'th dimension, ie dim[k]
m - position along the k'th dimension, a number between 1 and d

## 

